%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[twoside,twocolumn]{article}

\usepackage{blindtext} % Package to generate dummy text throughout this template 

\usepackage[numbers]{natbib}
\usepackage{dblfloatfix}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[utf8]{inputenc}	
\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
%\usepackage{subfigure}

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{multirow} 

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{The effect of short-term mindfulness focused attention meditation on pain sensitivity} %$\bullet$ May 2018} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage[hidelinks]{hyperref} % For hyperlinks in the PDF

\renewcommand{\thetable}{\Roman{table}}
\renewcommand{\thefigure}{\Roman{figure}}


%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{The effect of short-term mindfulness focused attention meditation on pain sensitivity} % Article title
\author{%
\textsc{Annabel Bantle, Irene Uriarte Mercader, Maria Kaalund Kroustrup}\\ % Your name
\textsc{and Toby Steven Waterstone}\\[1ex]
\normalsize Aalborg University \\ % Your institution
}

\date{May 31, 2018} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent
\textbf{Introduction:} Studies show that long-term mindfulness meditation provides the ability to enhance a broad spectrum of cognitive health outcomes on chronic pain patients. However, there are not many studies which show the effect of short-term mindfulness on chronic neck pain. The purpose of this study was to determine if short-term mindfulness focused attention meditation can alter pain sensitivity in healthy subjects. Even though the study was conducted in healthy subjects, the effects of meditation to pain sensitivity can be transferred to chronic pain patients.
\textbf{Methods:} 42 subjects were recruited for a control trial. To evaluate the pressure pain threshold and tolerance, pressure pain was applied with an algometer on the right upper trapezius in two measurements session with 5 days in between. The treatment group practiced 20 minutes of mindfulness focused attention meditation on 5 consecutive days between the two measurements, whilst the control group continued their normal 
routine. 
\textbf{Results:} Two-way mixed ANOVA showed no significant difference between control and treatment group in threshold (P = 0.321, P = 0.507) and tolerance (P = 0.080, P = 0.472). T-test showed no significant difference in the relative difference between first and second measurement of threshold (P = 0.149) and tolerance (P = 0.330). 
\textbf{Conclusion:} Nevertheless this study still contributes to the field of pain relief using mindfulness meditation. Since this study shows the tendency that mindfulness focused attention meditation increases both, threshold and tolerance, a longer period of practicing mindfulness focused attention meditation should be investigated.
\end{abstract}
}

%----------------------------------------------------------------------------------------

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\input{introduction}

%------------------------------------------------

\input{methods}

%------------------------------------------------

\input{results}

%------------------------------------------------

\input{discussion}

%------------------------------------------------

\input{conclusion}

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------


\footnotesize{\bibliographystyle{unsrt}
\bibliography{C:/Users/tobbe/Documents/GitHub/BMEI-2.sem/setup/BMEI_2.sem}


%\endgroup

%----------------------------------------------------------------------------------------

\end{document}
